---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# blueskynet

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/blueskynet)](https://CRAN.R-project.org/package=blueskynet)
<!-- badges: end -->

The purpose of blueskynet is to provide tools to generate and analyze networks from Bluesky Social.

## Installation

You can install the development version of blueskynet like so:

``` r
remotes::install_github("https://github.com/lassehjorthmadsen/blueskynet.git")
```

## Getting started

First, create an app password here: https://bsky.app/settings/app-passwords.

Then, set environment variable BLUESKY_APP_PASS to your app password, and another variable, BLUESKY_APP_USER, to your identifier (e.g. "lassehjorthmadsen.bsky.social") using `file.edit("~/.Renviron")`

Now, you can access the core function of `blueskynet`:

```{r example, message=FALSE, warning=FALSE}
library(blueskynet)
library(dplyr)

# Authenticate yourself
password <- Sys.getenv("BLUESKY_APP_PASS")
identifier <- Sys.getenv("BLUESKY_APP_USER")

# Then get a token and a refresh token
auth_object <- get_token(identifier, password)
token <- auth_object$accessJwt
refresh_tok <- auth_object$refreshJwt

# Establish a small net as a starting point
key_actor <- "natalieamiri.bsky.social"
keywords <- c("reporter", "journalist", "writer")
small_net <- init_net(key_actor, keywords, token)
```

First few rows of a starting point initial network:

```{r head}
small_net |> head(3)
```

When you're ready, you can build a bigger net, with several supporting artifacts, like a 3d-widget, using `build_network()` which we won't run here, since it can take a lot of time to build a big network.

## Example application

Have a look at a network of influential scientists on Bluesky Social, generated with `blueskynet` [here](https://lassehjorthmadsen.github.io/blueskyanalyses/).


## Documentation
`blueskynet` has a [pkddown](https://pkgdown.r-lib.org/index.html) website for documentation right [here](https://lassehjorthmadsen.github.io/blueskynet/index.html).
